Analysis paper

### 2021-05-17 analysis/analysis.Rmd
update analysis

truth_vs_forecast_2_deaths <- df %>%
  dplyr::filter(target_type == "death") %>%
  truth_and_obs_plot()  + 
  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[1:5])

@@

rel_skill_time_2_deaths <- scores_target_forecastdate %>%
  dplyr::filter(target_type == "death") %>%
  scores_over_time_plot() + 
  scale_color_brewer(palette = "Accent")

@@

# cases_plot <- truth_vs_forecast_2_cases / rel_skill_time_2_case + 
#   plot_layout(guides = "collect") & 
#   theme(legend.position = 'bottom') 
# 
# deaths_plot <- truth_vs_forecast_2_deaths / rel_skill_time_2_deaths + 
#   plot_layout(guides = "collect") & 
#   theme(legend.position = 'bottom')

truth_vs_forecast_2_cases / rel_skill_time_2_case / truth_vs_forecast_2_deaths / rel_skill_time_2_deaths + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

@@

```{r}
# scores by target type for 2 week ahead forecasts
scores <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "location_name", "forecast_date", 
                   "location_target", "classification"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[model != "Baseline"]

@@

```{r}
p <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges() + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ location_target) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
```

@@

@@

p / p_phases + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

>>>>

truth_vs_forecast_2_deaths <- df %>%
  dplyr::filter(target_type == "death") %>%
  truth_and_obs_plot()  + 
  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
  geom_rect(aes(xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf), fill = "lightgrey", alpha = 0.002)

@@

rel_skill_time_2_deaths <- scores_target_forecastdate %>%
  dplyr::filter(target_type == "death") %>%
  scores_over_time_plot() + 
  scale_color_brewer(palette = "Accent") + 
  geom_rect(aes(xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf), fill = "lightgrey", alpha = 0.002)

@@

# cases_plot <- truth_vs_forecast_2_cases / rel_skill_time_2_case + 
#   plot_layout(guides = "collect") & 
#   theme(legend.position = 'bottom') 
# 
# deaths_plot <- truth_vs_forecast_2_deaths / rel_skill_time_2_deaths + 
#   plot_layout(guides = "collect") & 
#   theme(legend.position = 'bottom') 
truth_vs_forecast_2_cases / rel_skill_time_2_case / truth_vs_forecast_2_deaths / rel_skill_time_2_deaths + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')

@@

```{r}
scores <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_type", "location_name", "forecast_date", 
                   "location_target", "classification"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[model != "Baseline"]

@@

```{r}

p_combined <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges() + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ target_type, ncol = 1) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))

p <- ggplot(scores, aes(y = model, x = scaled_rel_skill, 
                          group = model, fill = model)) + 
  ggridges::geom_density_ridges() + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  facet_wrap( ~ location_target) + 
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
```

@@

```{r fig.height=10, fig.width=15}
scores %>%
  gridExtra::tableGrob(theme = theme_minimal(), rows = NULL)
```

@@

(p_combined + p) / p_phases + 
  plot_layout(guides = "collect") & 
  plot_annotation(tag_levels = 'A') &
  theme(legend.position = 'bottom')
